{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-04-30 bmvc_review.tex
Revised the introduction and technical section.

\begin{figure*}[!t]
\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
\caption{The workflow of our Multiple KCF and Particle Filter based tracking method without the track re-detection module.}
\label{Workflow_figure}
\end{figure*}

In this study, we propose application of an ensemble of KCFs
in an intuitive way to perform robust scale-adaptive tracking at more
than $300$ fps. Our approach is inspired by \cite{ma2015long} where
two KCFs are employed as translation and scale filters. It first
estimates translation using the translation filter learned on
\textit{target}$+$\textit{background} area. Then, the scale filter
learned on the \textit{target} area is used to estimate new scale of
the target at the estimated position. Application of translation and
scale filter at each frame decreases run-time performance ($\leq50 fps$)
as we need to run detection on each scale candidate and perform training on both filters. Similarly,
we learn three different correlation filters specializing on different
aspects of tracking and addressing the weakness of each other,
resulting in more robust tracking. We name these filters as
\textit{target}+\textit{small background} translation filter
($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). The fig.~\ref{fig:Filters} shows the size of the ROIs associated with
$R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$ in addition to the hanning
windows assigned and desired Gaussian responses assigned to each one. Unlike \cite{ma2015long}, by running a single filter at
each frame, we can achieve the targeted operation frame rate. In our framework, each filter is only trained after it is run to estimate translation or scale. This makes more sense as neighboring frames show large correlation. Thus, skipping a few frames to train a filter does not result in dramatic information loss in the learned object model.

@@

Our MKCF based tracking framework employs different capabilities and
tasks to each correlation filter learned temporally. In
\cite{ma2015long, danelljan2014accurate}, a scale filter is learned on
\textit{target-only} area whereas \cite{henriques2015high,
  li2014scale, bibi2015multi, tang2015multi} uses a correlation filter
learned on \textit{target+background} area to find the optimal scale
in scale space. To learn the scale filter, $R_{s}$, we follow a
similar approach to \cite{ma2015long}. We believe that translation
filter needs to include background information to better discriminate
target from background, however, the goal of the scale filter is to
estimate the right size of the target, not to discriminate it from
background. Also, by using a smaller ROI we can reduce the template size
 to learn the scale filter, resulting in higher speed scale
estimation module and earning us some time to update scale. Finally, the scale filter help us on the track
re-initialization module which includes running an object proposals
algorithm to extract proposals from salient regions. By using the
scale filter in re-initialization module, we can reduce the
element-wise operations compared to the translation filters. Also, we can 
avoid false target re-initialization in the case of rapid background change as $R_{t}^{s}$ and
$R_{t}^{L}$ learn background in addition to target. The \textit{target+small background} area translation filter, $R_{t}^{S}$,
is assigned a larger template size than $R_{s}$ and smaller than
$R_{t}^{L}$. It estimates only translation similar
to \cite{henriques2015high}. Finally, the \textit{target+large
  background} area translation filter, $R_{t}^{L}$ , estimates translation of a target as $R_{t}^{S}$. We propose scale estimation at every $n$ number of frames using the scale filter. In our experiments on $OTB100$ and $UAV123$,
we observed that $n$ = 5 gives the best results in terms of precision and success overlap rates. The \textit{target+large background} translation filter is run
in the next frame after the scale filter as we want to avoid drifts which is more likely to happen running only $R_{s}$. Considering a large ROI for $R_{t}^{L}$ can degrade its performance due to information loss resulting from ROI resizing. On the other hand, only HoG features are used in $R_{t}^{S}$ as it focuses on a smaller ROI, giving us more discriminative HoG features. In our framework, $R_{t}^{S}$ addresses the absence of scale adaptation module in $R_{t}^{L}$ and $R_{t}^{S}$ whereas $R_{t}^{L}$ focuses on addressing the absence of translation estimation module in $R_{S}$. $R_{t}^{S}$, on the other hand, focuses on the shape features of the target that is not fully exploited in $R_{t}^{L}$ and $R_{t}^{S}$. For this reason, we employ \textit{HoG} features in $R_{t}^{S}$ and \textit{HoG} and \textit{Color} features in $R_{t}^{L}$. Fig.~\ref{Workflow_figure} displays the proposed tracking framework called Ensemble of KCFs {\it E}nKC. Also, the pseudo-code of the proposed {\it E}nKC is shown in alg.~\ref{alg:MKCF}.

@@

The Kernelized Correlation Filter tracker has recently been
increasingly popular due to its operation at hundreds of frames per
second with state-of-the-art tracking capabilities even in challenging
cases such as VOT15 dataset. Its computational efficiency arises from its use of the
discrete fourier transform of the circulant matrix and frequency
domain element-wise operations known as hadamard product and
division. The first example of frequency domain trackers is the Linear
Correlation Filter tracker known as MOSSE tracker. It minimizes the
ridge regression function in the frequency domain using a single
template with continous desired gaussian response. The KCF tracker, on
the other hand, minimizes the regularized ridge regression function
shown below.
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The $c$ parameter included in
\cite{henriques2015high,galoogahi2013multi} makes it possible to
integrate multi-channel features such as HoG and colour into the ridge
regression function. The closed-form solution for the
eq.~\ref{eq:Closedform_RidgeReg} can be obtained by setting the
derivative of $E$ w.r.t $w$ to $0$. The solution in the primal domain
can be formulated as
\begin{equation}
w = (X^{T}X+\lambda)^{-1}y
\label{eq:SpatialSolution}
\end{equation}
where $X$ and $\lambda$ represent the training samples and
regularization term. The same cost function in the Fourier domain can
be represented as
\begin{equation}
w = (X^{H}X+\lambda I)^{-1}X^{T}y
\label{eq:FourierSolution}
\end{equation}
More information on the spatial and fourier domain solutions can be
found in \cite{henriques2015high}. The MOSSE tracker does not make use
of $\lambda$ and only one training sample with desired response is
used to update $w$. This framework does not include enough background
information into the training framework with a single template. The
application of the circulant matrix theorem into the
eq.~\ref{eq:Closedform_RidgeReg} makes it possible to include many
background patches at a similar computational complexity. A circulant
matrix includes the circularly shifted patches of the positive
training sample $x$ by a cylic shift operator.

@@

\section{Particle Filter}
\label{sc:PF}
The proposed MKCF algorithm can cause undesired drift and noise in
tracking due to independent application of the correlation filters. To
mitigate the drift effect and reduce the noise, a Bayes Filter
representing the evolution of target's motion can be added into the
MKCF tracking framework. In this study, we consider a variant of a
Bayes Filter, \textit{Particle Filter}. The Particle Filter is a
Sequential Monte Carlo method that can approximate posterior
probability density functions (pdf) of a target motion. The
approximation becomes optimal with the infinite number of particles,
however, its run-time complexity grows exponentially with the number
of elements in the state space matrix, $X_{t}$. As the focus of this
study is to design a high speed tracker, we keep the number of state
space elements low and implement computationally cheap \textit{Weight
  Function} and \textit{Importance-Resampling} modules. We represent
the state space matrix as $X_{t} = \lbrace x,y,V_{x},V_{y}\rbrace$
where $x$ and $y$ are the centroid of the target and $V$ represents
the velocity components. We transit the particles with the well-known
first order Constant Velocity model. The centroid components are
applied Gaussian Noise whereas the velocity components are assigned
uniform noise representative of most of the objects. The observation
likelihood is modeled based on the confidence map of
$R_{t}^{L}$,$R_{t}^{S}$, and $R_{s}$. It can also be modeled based on
the euclidean distance between particle's centroid to the peak of the
confidence maps, however, we believe that the former approach could
result in further drifts in the case of multi-modal distributions. The
weights for the particles are computed with the bilinear interpolation
method.
\begin{equation}
	w_{p_{t}}(x_{t},y_{t}) = \dfrac{y_{R}(x_{t}-1,y_{t}-1)+y_{R}(x_{t}+1,y_{t}+1){y_{R}(x_{t}+1,y_{t}-1)+y_{R}(x_{t}-1,y_{t}+1)}}{4}
\end{equation}
where $w_{p}$ denotes the weight of the particle. The importance
re-sampling module is triggered when the number of effective particles
is smaller than a pre-defined threshold [Cite - Effective Number
  Samples Metric] to avoid variance getting too small. Re-sampling is
implemented with highly efficient low-variance ratio method
[cite]. Finally, the expected mean of the approximated posterior pdf
is computed as
\begin{equation}
	\hat{X}_{t} = \sum_{p=1}^{P}w_{p_{t}} X_{t}
\end{equation}

@@

WE SHOULD ASSIGN THE PRIOR WEIGHTS TO EXPECTED MEAN ESTIMATION OF THE
POSTERIORS WHEN THE RE-SAMPLING IS SKIPPED.
\section{Track Re-initilization via Re-detection}
\label{sc:Re-initialization}

%\section{Geometry Estimation between Target and Drone}
%\label{sc:Geometry}

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To verify the usefulness of our algorithm, we ran our algorithm using
two publicly available datasets: OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}, UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}. OTB100 dataset contains video sequences for 100 objects whereas UAV123 dataset contains aerial footage of 123 objects. The proposed $EnKCF$ method can better handle slow motions. Also, the UAVs use mobiles platforms with limited computational power. We believe that the proposed tracker can better fit to tracking from these platforms as it is highly efficient and scale adaptive. Taking into account these reasons, it is more appropriate to test it on aerial videos captured by UAVs.

>>>>

\begin{figure*}[!t]
\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
\caption{The workflow of the proposed {\it E}nKCF with a particle filter.}
\label{Workflow_figure}
\end{figure*}

In this paper, we extends the KCF in that multiple KCFs are deployed,
in turn, to address a target's scale change and dynamic maneuvers
while preserving the overall execution time very fast, i.e., $\ge$ 300
fps. The efficient nature of KCF computation results in a
small-footprint, executable. Such a fast execution will facilitate to
deploy the proposed algorithm on any embedded systems.

The proposed algorithm, {\it E}nKCF, deploys three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background twice bigger than that of the first filter, $R_{t}^{S}$,
\textit{target}+\textit{large background}. We set up {\it E}nKCF in
this way because we believe a correlation filter for learning a
target's translation should include its background to better
discriminate the target from its background and another correlation
filter is prepared to focus on the target itself to estimate the right
size or scale of the target. Figure \ref{fig:Filters} shows examples
of the region of interest (ROI) covered by each of three filters. We
believe that a filter for learning a target's translation should
include its background. In addition, making the ROI for the scale
filter, $R_{s}$, tighter reduces the size of the template for the
elementwise multiplication, resulting in a scale estimation in a
higher speed.

After Heriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high}, many variation of KCF were
investigated. In particular, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is particularly similar to that of
\cite{ma2015long} in that more than one KCF is used to address the
challenges of single target tracking. But ours is different from that
of \cite{ma2015long} in that we do not use those three KCFs together
at every frame, but alternatively at every three frame. The way our
algorithm is alternating multiple KCFs in different goals intuitively
makes sense in that the appearance of consecutive images does not
change much. Although it varies based on the scene, learning a
correlation filter a frame would not be much different from the one
learned using the image few or $k$ frames later. By alternating three
KCFs in turn, our algorithm runs as fast as or faster than the
original KCF. From our experiments, we empirically found that five is
the optimal for $k$ in terms of precision and success rates. We'll
detail this at the experimental section later.

@@

The order of deploying these three KCFs is {\it Burak: Answer this}

The \textit{target+large background} translation filter, $R_{t}^{L}$,
is designed to run in right next frame after the scale filter,
$R_s$. We deploy these two filters in this way because we want to
minimize any drifts, which are likely to happen running only $R_{s}$.

{\it Burak: Rewrite the following two sentences.}

Considering a large ROI for $R_{t}^{L}$ can degrade its performance
due to information loss resulting from ROI resizing.

On the other hand, only HoG features are used in $R_{t}^{S}$ as it
focuses on a smaller ROI, giving us more discriminative HoG
features.

The reason why our {\it E}nKCF comes with two KCF for translation {\it
  Burak: Answer this.}

In our framework, $R_{t}^{S}$ addresses the absence of scale
adaptation module in $R_{t}^{L}$ and $R_{t}^{S}$ whereas $R_{t}^{L}$
focuses on addressing the absence of translation estimation module in
$R_{S}$.

$R_{t}^{S}$, on the other hand, focuses on the shape features
of the target that is not fully exploited in $R_{t}^{L}$ and
$R_{t}^{S}$. For this reason, we employ \textit{HoG} features in
$R_{t}^{S}$ and \textit{HoG} and \textit{Color} features in
$R_{t}^{L}$. Fig.~\ref{Workflow_figure} displays the proposed tracking
framework called Ensemble of KCFs {\it E}nKC. Also, the pseudo-code of
the proposed {\it E}nKC is shown in alg.~\ref{alg:MKCF}.

@@

\subsection{Kernelized Correlation Filter} \label{sec:kcf}
The Kernelized Correlation Filter tracker has recently been
increasingly popular due to its operation at hundreds of frames per
second with state-of-the-art tracking capabilities even in challenging
cases such as VOT15 dataset. Its computational efficiency arises from
its use of the discrete fourier transform of the circulant matrix and
frequency domain element-wise operations known as hadamard product and
division. The first example of frequency domain trackers is the Linear
Correlation Filter tracker known as MOSSE tracker. It minimizes the
ridge regression function in the frequency domain using a single
template with continous desired gaussian response. The KCF tracker, on
the other hand, minimizes the regularized ridge regression function
shown below.
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The $c$ parameter included in
\cite{henriques2015high,galoogahi2013multi} makes it possible to
integrate multi-channel features such as HoG and colour into the ridge
regression function. The closed-form solution for the
eq.~\ref{eq:Closedform_RidgeReg} can be obtained by setting the
derivative of $E$ w.r.t $w$ to $0$. The solution in the primal domain
can be formulated as
\begin{equation}
w = (X^{T}X+\lambda)^{-1}y
\label{eq:SpatialSolution}
\end{equation}
where $X$ and $\lambda$ represent the training samples and
regularization term. The same cost function in the Fourier domain can
be represented as
\begin{equation}
w = (X^{H}X+\lambda I)^{-1}X^{T}y
\label{eq:FourierSolution}
\end{equation}
More information on the spatial and fourier domain solutions can be
found in \cite{henriques2015high}. The MOSSE tracker does not make use
of $\lambda$ and only one training sample with desired response is
used to update $w$. This framework does not include enough background
information into the training framework with a single template. The
application of the circulant matrix theorem into the
eq.~\ref{eq:Closedform_RidgeReg} makes it possible to include many
background patches at a similar computational complexity. A circulant
matrix includes the circularly shifted patches of the positive
training sample $x$ by a cylic shift operator.

@@

\subsection{Particle Filter} \label{sc:PF}
The proposed MKCF algorithm can cause undesired drift and noise in
tracking due to independent application of the correlation filters. To
mitigate the drift effect and reduce the noise, a Bayes Filter
representing the evolution of target's motion can be added into the
MKCF tracking framework. In this study, we consider a variant of a
Bayes Filter, \textit{Particle Filter}. The Particle Filter is a
Sequential Monte Carlo method that can approximate posterior
probability density functions (pdf) of a target motion. The
approximation becomes optimal with the infinite number of particles,
however, its run-time complexity grows exponentially with the number
of elements in the state space matrix, $X_{t}$. As the focus of this
study is to design a high speed tracker, we keep the number of state
space elements low and implement computationally cheap \textit{Weight
  Function} and \textit{Importance-Resampling} modules. We represent
the state space matrix as $X_{t} = \lbrace x,y,V_{x},V_{y}\rbrace$
where $x$ and $y$ are the centroid of the target and $V$ represents
the velocity components. We transit the particles with the well-known
first order Constant Velocity model. The centroid components are
applied Gaussian Noise whereas the velocity components are assigned
uniform noise representative of most of the objects. The observation
likelihood is modeled based on the confidence map of
$R_{t}^{L}$,$R_{t}^{S}$, and $R_{s}$. It can also be modeled based on
the euclidean distance between particle's centroid to the peak of the
confidence maps, however, we believe that the former approach could
result in further drifts in the case of multi-modal distributions. The
weights for the particles are computed with the bilinear interpolation
method.
\begin{equation}
	w_{p_{t}}(x_{t},y_{t}) = \dfrac{y_{R}(x_{t}-1,y_{t}-1)+y_{R}(x_{t}+1,y_{t}+1){y_{R}(x_{t}+1,y_{t}-1)+y_{R}(x_{t}-1,y_{t}+1)}}{4}
\end{equation}
where $w_{p}$ denotes the weight of the particle. The importance
re-sampling module is triggered when the number of effective particles
is smaller than a pre-defined threshold [Cite - Effective Number
  Samples Metric] to avoid variance getting too small. Re-sampling is
implemented with highly efficient low-variance ratio method
[cite]. Finally, the expected mean of the approximated posterior pdf
is computed as
\begin{equation}
	\hat{X}_{t} = \sum_{p=1}^{P}w_{p_{t}} X_{t}
\end{equation}

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To verify the usefulness of our algorithm, we ran the proposed
algorithm against two publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}},
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}. OTB100
dataset contains video sequences for 100 objects whereas UAV123
dataset contains aerial footage of 123 objects.

The proposed $E$nKCF method can better handle slow motions. Also, the
UAVs use mobiles platforms with limited computational power. We
believe that the proposed tracker can better fit to tracking from
these platforms as it is highly efficient and scale adaptive. Taking
into account these reasons, it is more appropriate to test it on
aerial videos captured by UAVs.
